Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-24 draft/ms_v4.tex
New figure1 and some edits

    %
    These challenges are not merely technical details; their resolution is crucial
    to achieving key scientific goals.
    For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001})
    is a powerful tool for measuring the large-scale distribution of dark matter.
    However, WL measurements critically depend on our ability to measure the shape and photometric redshifts of background galaxies with high precision. Photometric redshifts (e.g., \citealt{Benitez2000, Bolzonella2000,
    Ilbert2009}) are fundamentally important for studying the evolution of galaxies,
    and the ``drop-out'' method is critical for selecting high-redshift galaxies
    (e.g., \citealt{Steidel1996}).
    However, both of those methods reply on the availability of accurate multi-band photometric
    measurements. With increasingly large surveys,  and with more stringent requirements on data quality,  quality control also becomes a pressing issue.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of the main steps involved in using \synpipe{}.
        Gray boxes indicate required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects synthetic objects into single-frame images. Below the blue box, we show an HSC image before and after the insertion of synthetic galaxies. The positions of synthetic  objects are highlighted with green circles. Red boxes depict the image coadding and multi-band measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py}. At the bottom left, we show a \coadd{} image which contains synthetic galaxies. On the right hand side, we show the spatial relation
        between \texttt{Tracts}, \texttt{Patches}, and \texttt{Visits}. 
        The red colored box corresponds to one \texttt{Tract} which has an area of 
        about 1.5 deg$^2$. 
        Large colored circles are \texttt{Visits} (also commonly known as "pointings") 
        with small rectangles representing CCDs. 
        \texttt{Patches} are represented by black dashed lines. 
        One \texttt{Tract} typically contains 81 \texttt{Patches}.}
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %%
    These challenges are not merely technical details; their resolution is crucial
    to achieving key scientific goals.
    For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001})
    is a powerful tool for measuring the large-scale distribution of dark matter.
    However, WL measurements critically depend on our ability to measure the shape and 
    photometric redshifts of background galaxies with high precision. 
    Photometric redshifts (e.g., \citealt{Benitez2000, Bolzonella2000, Ilbert2009}) are 
    fundamentally important for studying the evolution of galaxies, and the ``drop-out'' 
    method is critical for selecting high-redshift galaxies 
    (e.g., \citealt{Steidel1996}).
    However, both of those methods rely on the availability of accurate multi-band 
    photometric measurements. 
    With increasingly large surveys, and with more stringent requirements on data 
    quality, quality control also becomes a pressing issue.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of the main steps involved in using \synpipe{}.
        Gray boxes indicate required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
        synthetic objects into single-frame images. 
        Below the blue box, we show an HSC image before and after the insertion of 
        synthetic galaxies. 
        The positions of synthetic objects are highlighted with green circles. 
        Red boxes depict the image coadding and multi-band measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py}. 
        At the bottom left, we show a \coadd{} image which contains synthetic galaxies. 
        On the right hand side, we show the spatial relation between \texttt{Tracts},
        \texttt{Patches}, and \texttt{Visits}. 
        The red colored box corresponds to one \texttt{Tract} which has an area of 
        about 1.5 deg$^2$. 
        Large colored circles are \texttt{Visits} (also commonly known as "pointings") 
        with small rectangles representing CCDs. 
        \texttt{Patches} are represented by black dashed lines. 
        One \texttt{Tract} typically contains 81 \texttt{Patches}.
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%
